Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2025-02-10 demystify.tex
updates

Of course my recommendation is just one of the three or four faculty who review the application.  The adcom chair will compile all recommendations and make a decision based on them (\autoref{sec:adcom-discuss}).
If there are disagreements, adcom chair will ask the reviewers to discuss the application. 
Unfortunately, even if all revierwers recommend a student, they might not be admitted (\autoref{sec:why-rejected}) if there are too many students or they are not a good fit for the program (e.g., no one is willing to advise them).

@@

As AI/LLMs become more popular, many students wonder if they could use it to help with their statements and university/adcom reviewers would check and penalize AI-assisted writing.

>>>>

Of course my recommendation is just one of the three or four faculty who review the application.  The adcom chair will compile all recommendations and make a decision based on them (\autoref{sec:adcom-discuss}).
If there are disagreements, adcom chair will ask the reviewers to discuss the application. 
Unfortunately, even if all reviewers recommend a student, they might not be admitted (\autoref{sec:why-rejected}) if there are too many students or they are not a good fit for the program (e.g., no one is willing to advise them).

@@

As AI/LLM's become more popular, many students wonder if they could use it to help with their statements and university/adcom reviewers would check and penalize AI-assisted writing.
